% ============================================================
\section{Conclusions and Future Work}
\label{sec:future}
% ============================================================

Wave Guide shows that systematic, explainable playlist generation is achievable on open-source infrastructure. The system encodes 11 compatibility dimensions grounded in music cognition research, navigates the ListenBrainz similarity graph via bidirectional beam search, satisfies hard and soft constraints through local search, and explains every decision at three levels. Key lessons: multi-dimensional similarity is essential for natural transitions, explainability builds user trust, fallback mechanisms are critical for data gaps, and self-hosting Postgres pays off despite setup cost.

\paragraph{Near-term work.} Two items planned but not merged into \texttt{main} by submission are top priority. First, end-to-end wiring of mood-based input directly into the search algorithm: Module~4 already exposes \texttt{get\_centroid\_track(mood)} and the demo uses mood labels to filter the track-picker UI, but the search itself still anchors on MBIDs. A small orchestrator (50--80 lines plus accepting \texttt{source\_mood} / \texttt{dest\_mood} on \texttt{/api/playlist}) would let beam search use a mood centroid as either endpoint directly; a prototype of this wiring exists on a feature branch. Second, the energy function uses Gaussian decay over raw spectral values with $\sigma=0.003$, calibrated on four tracks; log-normalising each band against empirical AcousticBrainz ranges (Weber's law) yields more stable 0--1 scores across genres and lets the existing mood-derivation thresholds fire correctly.

\paragraph{Longer-term.} Batch Essentia extraction for popular tracks reduces the 5--10~s fallback latency. Human-annotated mood labels would raise the 64.7\% classifier ceiling. Hybrid graph/content-based search mitigates cold-start for tracks absent from the ListenBrainz graph. LLM-enhanced explanations would replace template prose. Cross-modal queries (text, hummed melodies), skip-aware real-time adaptation, and collaborative multi-user playlists are natural extensions of the current architecture.

\vspace{1em}
\noindent\textbf{Repository:} \url{https://github.com/Alvin-Furman-CS-Classroom/project-2-ai-system-rocking-rolling}

\noindent\textbf{Demo:} [Ask team for demo URL]
