% ============================================================
\section{Proposal Delta}
% ============================================================

The implementation diverged from the original proposal in seven concrete ways.

\paragraph{MusicBrainz data source.} The proposal assumed direct use of the public MusicBrainz REST API. The 1~req/sec rate limit proved prohibitive for multi-hop graph traversal, so we deployed a self-hosted Postgres mirror of the MusicBrainz database, which enables batch joins and yields a 2.74$\times$ speedup on relationship queries. The mirror also enabled a canonical song search API that the MusicBrainz REST API does not support: given a track title, the query returns the MBID of the most well-known release (ranked by release date and label prestige), making it substantially more likely that downstream AcousticBrainz and ListenBrainz lookups for that MBID will succeed.

\paragraph{Audio feature extraction.} The proposal relied solely on AcousticBrainz. Because AcousticBrainz was archived in 2022 and its API is subject to severe throttling, we added an Essentia-based local fallback; Essentia was invoked for approximately 12\% of tracks where AcousticBrainz data was unavailable or too slow to retrieve.

\paragraph{Search algorithm.} Beam search was proposed from the outset, but two implementation details were not. First, the search is bidirectional, expanding from both source and destination simultaneously to halve the effective search depth. Second, when the local frontier is exhausted, the system queries ListenBrainz for similar recordings to widen the candidate pool---a dynamic neighborhood lookup that was not part of the original design.

\paragraph{Feature dimensionality.} The original four compatibility dimensions were expanded to eleven, informed by the music information retrieval literature and the available data from AcousticBrainz~\cite{knees2013,korzeniowski2021,schweiger2025}.

\paragraph{Explanations.} The proposal included no explanation layer. We added a three-level explanation system covering per-transition component scores, constraint scorecards, and an auto-generated journey summary.

\paragraph{Mood integration.} The proposal called for mood input to be wired directly into the search algorithm as a search anchor. Module~4 was fully trained, reaching 64.7\% single-split validation accuracy and 65\% mean 5-fold CV accuracy, and its class centroids are exposed via API. However, integrating the centroid as a beam-search anchor proved complex; in the current demo, mood is used only to filter the UI track picker, and the underlying search remains MBID-to-MBID.

The four-module architecture, exclusive use of the MetaBrainz ecosystem, the Flask + React stack, and the constraint-satisfaction approach all remained consistent with the proposal.